--- 
title: Report of the Exploratory Data Analysis
---

Group Members: Chloe Gao, Xuchen Chen, Jung Hwan Lee, Shenhan Xu.

>Introduction

The domain of our final project is related to the books. The reason that we choose this domain is that we are all fond of reading. Books play a quintessential role in everyone’s life by introducing them to a world of imagination, providing knowledge of the outside world, improving their reading, writing, and speaking skills as well as boosting memory and intelligence. We believe that a list of the bestselling books will not only bring people a guide to know more good books but also give people insight into how other people live by broadening their worldview. We hope to find out what books are the most popular among people by this opportunity. With the knowledge that we will process the data, we can find an easier approach to finding the books we may be interested in based on the title, the category, and the review rate.

>Summary

In the summary section, we found that there are 700 observations in this dataset, 312 books are fiction, and 388 books are non-fiction. In these 700 books, we observed that *Where the Crawdads Sing* has the maximum number of reviews, which is 208917. Moreover, we compared the user rating (out of 5 stars) and the price of the fiction and non-fiction. We found that the average user rating for fiction is 4.66, and the average user rating for non-fiction is 4.62. The user rating for fiction is slightly lower than non-fiction. Also, we calculated the average price of fiction and non-fiction; fiction has an average price of 10.7 dollars, and non-fiction has a price of 14.3 dollars. It is also interesting to generate the tendency of the user rating by years. By analyzing the rates, we discovered that the user rating is tending to be higher and higher by year, from 4.58 in 2009 to 4.69 in 2022. We pondered that the fact has shown that the quality of the book contents is getting better so that people would like to read and rate high. Lastly, we detected that the price of the books is getting lower over years, from 15.4 dollars to 12.5 dollars. We would like to say that this is a good tendency because it makes reading become more accessible for everyone, which means more people will buy books to read since the price is low. 

>Table

```{r, echo=FALSE, eval=TRUE, code = readLines("table.r")}
```

The table we created for this data set mainly focuses on the book genre (fiction/non-fiction), book rating, book price, and released year. The reason that we chose these four categories is that these are basic information about the book, and it is easier to discover the tendency when any one of the categories is fixed. For example, when we have the genre is fixed in the table, we will be able to see and summarize the comparison of the price of the fiction and non-fiction, or the user rate changing between the two. 

>Charts

```{r, echo=FALSE, eval=TRUE, code = readLines("charts.r")}
```
The first chart we created for this data set is to discover the relationship between the released year and book genres. From the bar graph, it is easy to see that there is a similar amount of fiction and non-fiction released each year from 2009 to 2020. In our opinion, this is a good balance; it shows that there is no distinct deviation between the reader choosing fiction and non-fiction.

The second chart we created displays the relationship between user ratings and the number of books from our book list. From the left-skewed histogram, we will be able to see that the majority of the book rating is between 4.5 to 5.0. Also, the x-axis scale shows that the average score in this book list is relatively high, most likely from 4.0 - to 5.0; this is a good reason why they are on this bestselling book list. From our perspective, user rating is a crucial element to consider whether a book is supposed to be collected in a book list. An authentic user rating reflects the true evaluation of the public. Hence, we created this histogram to show the tendency of the user rating.

We also created a table to reflect the relationship between the number of reviews and ratings of different book genres. From the scale of the y-axis (number of reviews), we can tell that many readers would like to provide reviews and comments for their preferred books. We think that the greater number of reviews indicates that this book list data set is reliable. Moreover, the graph of the fiction and non-fiction in this diagram also shows that readers tend to rate more fiction with higher scores. Since we have analyzed the amount of the fiction and non-fiction are similar, we found that readers are more likely to rate non-fiction, which represents that people would like to read more non-fiction today. 

>Conclusion

In conclusion, we made a big progress in this exploratory data analysis. This report has shown and solved the questions that our group was curious about and concerned about, such as the book price changing and user rating reflection. We put efforts on summarizing and making table and charts from our chosen data set, and we also learned to flexibly utilize the skills from class. 